CLT Results

### 2022-04-05 analysis/clt_irt_analysis.Rmd
minor tweeks

```
```{r}
params%>%left_join(coefs2PL)%>%
  mutate(slope = ifelse(nlpar == "Easiness", -1,1))%>%
  ggplot(aes(x = Estimate, y = par))+
  geom_abline(aes(slope = slope, intercept = 0), lty = 3, alpha = .5)+
  geom_errorbar(aes(ymin = CI_2.5, ymax = CI_97.5), alpha = .25, col = "dodgerblue")+
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), alpha = .25, col = "dodgerblue")+
  geom_point(pch = 1, alpha = .75)+
  facet_grid(~nlpar)+
  labs(x = "Bayesian estimate", y = "Frequentist estimate")+
  stat_cor()+
  ylim(-10,10)+
  #xlim(-10,10)+
  #coord_fixed(ratio = 1)+
  scale_color_viridis_c()+
  theme_bw()
```
# Correlation subtest and full test

```{r}
select <-params %>%
  pivot_wider(names_from = nlpar, values_from = Estimate)%>%
  arrange(
    #Easiness, 
    -Discrimination
    )%>%
  slice(1:15)#%>%
  pull("item")

>>>>

```{r}
params%>%left_join(coefs2PL)%>%
  mutate(slope = ifelse(nlpar == "Easiness", -1,1))%>%
  ggplot(aes(x = Estimate, y = par))+
  geom_abline(aes(slope = slope, intercept = 0), lty = 3, alpha = .5)+
  geom_errorbar(aes(ymin = CI_2.5, ymax = CI_97.5), alpha = .25, col = "dodgerblue")+
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), alpha = .25, col = "dodgerblue")+
  geom_point(pch = 1, alpha = .75)+
  facet_grid(~nlpar)+
  labs(x = "Bayesian estimate", y = "Frequentist estimate")+
  stat_cor()+
  ylim(-10,10)+
  xlim(-10,10)+
  #coord_fixed(ratio = 1)+
  scale_color_viridis_c()+
  theme_bw()
```
# Correlation subtest and full test

```{r}
select <-params %>%
  pivot_wider(names_from = nlpar, values_from = Estimate)%>%
  arrange(
    Easiness, 
    #-Discrimination
    )%>%
  slice(1:15)%>%
  pull("item")
